Full Article Review

### 2024-08-14 doc/reviews/luke.qmd
started reviewing some of the papers

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

-   Onboarding
-   Documentation
-   Contributing
-   Centralization
-   Knowledge management
-   Communication
-   Guidelines

@@

-   Guide

@@

This paper seems more targeted to general open projects and not strictly
about open collaboration within research. However, it is useful
information contained within on some general steps to take to encourage
and continue collaboration in open projects and in as open ways as
possible.

The rules that are more relevant to open collaboration are:

1.  Be welcoming: Example, recognize when newcomers join and have an
    onboarding process or document.
2.  Make governance explicit: Example, how are decisions made?
3.  Keep knowledge up to date and findable: Example, where are the
    contributing guidelines?
4.  Have a code of conduct that you enforce: Example, what are the
    guidelines for communication and what happens if someone breaks
    them?
5.  Make it easy for contributors to get started: Example, like the
    being welcome, have an onboarding document and/or roadmap for the
    projects work.
6.  Acknowledge all contributions: Any contribution can be meaningful if
    it helps further the goal of the project.

@@

-   Data infrastructure
-   FAIR data
-   Case study
-   Agile design
-   Templates
-   Examples
-   Strategies
-   Software development

@@

-   Case study
-   Example workflow

@@

-   While the project's output is a data sharing platform, the process
    to get there required a high level of collaboration.
-   Seems to use GitHub to at least build the website.
-   Building up an open collaboration project takes years of continued
    work and effort.
-   Took a multi-staged approach to establishing the group/community.
    -   At each stage, it was slowly about introducing the concepts to a
        broader and broader audience and getting feedback all along the
        way.
-   Development follows principles of agile software development by
    getting requirements from users, designing and developing those
    requirements, seeking feedback from users on what was developed, and
    testing the developed features.
-   Use of the iterative development helped them identify and respond to
    issues that came up. This is something that could be something that
    non-software projects could use to help with collaboration and
    maintaining momentum and motivation.

@@

-   Large-scale collaboration
-   Data aggregation
-   Replications
-   Limited resources
-   Strategies
-   Case study
-   Communities of practice

@@

-   Example workflow
-   Community building
-   Case study

@@

-   Mostly an example of what they did and why
-   Faced with limited resources and small sample sizes, but
    wanting/needing more to make results generalizable, they put
    together this collaboration project.
-   Outlines benefits of this collaboration, such as reducing the
    efforts of individual researchers by distributing workload,
    resources, and knowledge sharing/creation/management.
-   Challenges to this collaboration are less papers, lower ability to
    cover more topics, less freedom of control and direction at the
    individual researcher level (since they are part of a larger group
    and need to have a consensus on a topic or standards of practice),
    higher level of rules and processes for dealing with researchers who
    try to take advantage of the community for their own benefit, as
    well as how to decide on authorship/contributorship for scientific
    publications.
    -   A big challenge to these collaborations is sources of funding.
        Who pays for whose salary? How are funds distributed?
-   Argues that any large-scale collaboration needs to use open
    practices by default.
-   Something to consider when building large-scale collaboration is its
    continuation. If its started by one or a few people and with
    dedicated funding for it, what happens if that person or people
    leave or move on to other things? Or when the funding ends? These
    need to be considered at the start.
-   The ManyPrimates use GitHub, at least to host their website with
    some general documentation and guidelines, as well as some analysis
    code and data for some papers they've published.
-   The ManyPrimates project also set some basic standards for project
    file and folder structure, for pre-registering the study, etc.
